---
title: "Digitalization and the Organization of Work in the Digital Government Research Library v17.5: A Structural Topic Model"
author: "Andres Aguilera Castillo"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  pdf_document: default
  html_document: default
bibliography: references.bib
---

```{r data, include = FALSE}
library(readr)
library(dplyr)
library(here)
library(naniar)
# Import DGRL version 17.5 (2021/12/15) 16531 References
# https://faculty.washington.edu/jscholl/dgrl/index.php 
# RIS file format converted to CSV using Zotero Reference Manager
DGRLv17_5_zotero <- read_csv(here("data", "DGRLv17.5_zotero.csv"))
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Abstract

Digital Government is a growing and vibrant multidisciplinary field of research, the fast increase in research output has challenged researchers to explore and use novel computational ways and methods to perform evidence synthesis on the extant literature and be able to map a scientific discipline, explore the thematic evolution over time and identify potential avenues for further research. The exploration of the linkages between digitalization and the organization of work remains relatively unexplored in a public sector context. Topic modeling has emerged as a powerful computational technique that contributes to the examination of large amounts of text data. This chapter aims to perform a 'smart literature review' on a subset of the Digital Government Reference Library (DGRL) version 17.5, by using text as data approach and a topic modeling technique known as Latent Dirichlet Allocation (LDA). To our best knowledge, this is the first attempt to use unsupervised machine learning techniques with this data set. This effort may contribute to creating a map of the field, identify the evolving themes in the literature and help to identify promising areas of research.

## Introduction

Recent trends in global scientific output demonstrate a rapid and sustained increase in the production of vast amounts of unstructured data in the form of digitized text. This bounty in research content is challenging researchers to explore and pursue novel methodological approaches and techniques to examine massive volumes of scientific publications. Essentially, the ever-growing amounts of bibliographic information available in almost any field of research exceed human capacity making it necessary to explore computational-assisted approaches for research synthesis. Studies in the history of science have identified a relatively sustained growth pattern in scientific publications over time, this exponential growth rate means a doubling in scientific output every 17 years approximately [@bornmann2021]. This level of growth might be attributed to the increased resources dedicated to the global scientific endeavor and consequently the communication of science via publications. However, it may also be due to what has been dubbed "salami sliced publishing" or the multiple publications of a single research study [@bornmann2007a; @bornmann2015].

Digital Government Research (DGR) as a multidisciplinary research field is experiencing rapid growth in its research output. Contributions to this research domain come from established disciplines such as information science, computer science, organization science, sociology, public administration, and political science [@scholl2021]. The diversity in scope and methods of these disciplines converge in the field of Digital Government enriching it, but at the same time, raising questions as regards the lack of native theoretical developments, thus relying upon frameworks, theories, and conceptualizations from related disciplines [@bannister2015].

The advent of computerization and digitalization has had broad impacts in most aspects of contemporary life, including scientific research. Digitalization has influenced how research is designed and conducted, allowing for the creation and increased availability of ever-growing data sets that require powerful computational methods and enhanced tools to handle abundant information [@meyer2015]. Case in point is unsupervised machine learning techniques for text analysis, this research technology can be used in a wide range of disciplines to examine databases, repositories and corpora thus expanding the methodological repertoire of scholars and opening an opportunity to explore large troves of data.

Research synthesis is part of the literature review process in which the extant scientific knowledge in each academic field is examined to help scholars understand the conceptual structure, themes, and debates to identify trends in the literature and potential areas for further research. This crucial task is labor-intensive, time-consuming, and restricted to a limited number of documents if conducted by traditional "manual" methods [@antons2020a; @asmussen2019]. Still, computer-assisted text analysis does not substitute human intervention, instead it "augments our reading ability" [@grimmer2022], human judgement is deemed necessary for the evaluation and validation of the outcome of these models [@barberá2021].

```{r number and type of references in DGRLv17.5, include = FALSE}
rows_DGRLv17_5 <- nrow(DGRLv17_5_zotero)
```

This chapter explores the contents of The Digital Government Research Library in its version 17.5 (Scholl, 2021a), using a text as data approach and an unsupervised machine learning technique known as Latent Dirichlet Allocation (LDA). In its raw form, version 17.5 of the dataset contains `r rows_DGRLv17_5` references related to the Digital Government Research (DGR) domain, the most prevalent categories of references are conference papers (33%) and journal articles (50%). Previous explorations of this reference library using bibliometric and scientometric approaches have revealed the thematic evolution (Alcaide--Muñoz et al., 2017), and identified the most influential journals, conferences and leading scholars in the field (Scholl, 2021b). To our best knowledge this is the first attempt to run a topic model for a corpus in the field of Digital Government Research.

Scholars exploring labor-saving technologies have applied similar techniques expanding the methodological repertoire available and inspiring a similar pursuit for the exploration of the impact of technological change in a public sector context [@arduini2014; @montobbio2022].

RQ

Process

```{r dgrl_v175, include = TRUE}
summary(DGRLv17_5_zotero)
```

# Literature Review // Conceptual framework

You can also embed plots, for example:

## Methods and Data

The Digital Government Research Library version 17.5 is a large curated repository of publications contributing to the field of Digital Government Research (DGR), in its raw form this version of the library has `r rows_DGRLv17_5` references, the lion's share being journal articles n=8278 and conference papers n=5493. 

```{r types of documents}
by_type <- DGRLv17_5_zotero %>% count(`Item Type`) %>% arrange(desc(n))
by_type
```

```{r missing}
vis_miss(DGRLv17_5_zotero, warn_large_data = FALSE)
miss_all_db <- pct_miss(DGRLv17_5_zotero)
```

The data set has a large proportion of missing values `r miss_all_db` but not all columns are relevant to this exploration. 

By visually exploring a reduced version of the dataset, it is evident that a large amount of relevant information is missing. 

The workflow for reproducibility includes text pre-processing meaning data cleaning and data transformation. Some variables of interest are missing and there must be some data preparation before running creating a corpus.

## Results

## Discussion

## Conclusions

## References
